
---
title: "histograms"
author: "amesclir"
date: "06/17/2015"
output: html_document
---

First, we are going to perfom the the comparison between C. furva and its sister clade. 

```{r}
#Mutational between haplotypes in the C. furva's sister clade
sister<-c(10,12,9,14,15,12,10,9,16,16,19,15,4,3,6,7,5,6,1,8,8,11,7,5,8,9,7,8,3,10,10,13,9,7,8,6,7,2,9,9,12,8,9,9,10,5,12,12,15,9,10,11,6,13,13,16,12,9,4,11,11,14,10,5,12,12,14,10,7,7,10,6,8,13,9,13,9,8)

#Mutational between haplotypes in the C. furva
furva<-c(2,8,3,1,1,5,10,1,3,3,7,11,7,9,3,4,4,8,2,4,6)
```

Now we are going to plot ther frequency of the mutational steps among species in the sister clade vs within C.furva

```{r}
set.seed(42)
p1 <- hist(sister, breaks = 19)                     # centered at 4
p2 <- hist(furva, breaks = 11)                     # centered at 6
plot( p1, col=rgb(0,0,1,1/4), xlim=c(0,20), main = "C. furva clade vs. sister clade", xlab = "mutational steps")  # first histogram
plot( p2, col=rgb(1,0,0,1/4), xlim=c(0,20), add=T)  # second
```

Then, Finally, we are going to perfom another triple comparison: 1. C. furva within lineages, C. furva between lineages and among species in C. furva sister clade. Note: The lineages are H3 vs. the rest. 

```{r}

#mutational steps between C.furvaH3 and the rest
furva.H3<-c(8,10,11,7,9,3)

#mutational steps among haplotypes of C. furva excluding H3
furva.noH3<-c(2,3,1,1,5,1,3,3,7,4,4,8,2,4,6)

```

Now we are going to plot the frequency of the mutational steps.

```{r}
set.seed(42)
p1 <- hist(sister, breaks = 19)                     # centered at 4
p2 <- hist(furva.H3, breaks = 11)                     # centered at 6
p3 <- hist(furva.noH3, breaks = 8)
plot( p1, col=rgb(0,0,1,1/4), xlim=c(0,20), main = "C. furva H3 clade vs. C. furva no H3 clade  vs. sister clade", xlab = "mutational steps")  # first histogram
plot( p2, col=rgb(1,0,0,2/4), xlim=c(0,20), add=T)  # second
plot( p3, col=rgb(0,1,0,2/4), xlim=c(0,20), add=T)  # second
```


Finally, we are going to perfom another triple comparison: 1. C. furva within lineages, C. furva between lineages and among species in C. furva sister clade. Note: The lineages are H3+H7 vs. the rest. 

```{r}

#mutational steps among lineages
furva.among <- c(4,5,6,7,7,8,8,9,10,11)

#mutational steps within lineages
furva.within<-c(2,3,1,1,1,3,3,4,4,2,3)

```


Now we are going to plot the frequency of the mutational steps.

```{r}
set.seed(42)
p1 <- hist(sister, breaks = 19)                     # centered at 4
p2 <- hist(furva.among, breaks = 7)                     # centered at 6
p3 <- hist(furva.within, breaks = 4)
plot( p1, col=rgb(0,0,1,1/4), xlim=c(0,20), main = "C. furva among clade vs. C. furva witin  vs. sister clade", xlab = "mutational steps")  # first histogram
plot( p2, col=rgb(1,0,0,2/4), xlim=c(0,20), add=T)  # second
plot( p3, col=rgb(0,1,0,2/4), xlim=c(0,20), add=T)  # second
```
